---
title: "F1 Stat Vignette"
author: "Simge Cinar & Hugo Morvan"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


Calling the necessary functions
```{r}
setwd("..")  
source("R/functions.R")
```

Note that I used invisible() function while calling some function to preventing the getting the duplicate output

## Driver API functions

This functions returns the data as a list from the API
```{r}
driver_API(2012)
```

This function takes the list from the function driver_API, convert that list to a dataframe and select the columns which are necessart
```{r}
driver_get_df(2012)
```

This function returns the driver who won most races in that year, their number of wins and their number of points 
```{r}
invisible(driver_winner(2012))
```

This function creates and return a data.frame for the driverStandings API for the years between 'from' and 'to'
```{r}
driver_btw_years(2012, 2015)
```

Gives the driver with the most wins during a given period [from-to]
```{r}
invisible(driver_winner_period(2012, 2015))
```


## Constructor API Functions

This function gets the raw data from the constructorStandings API for a specific year and returns a list
```{r}
const_API(2016)
```

This function fetches the information from the const_API() function and converts it into a data.frame
```{r}
const_get_df(2016)
```

Find the Constructor who won the most races in the given year
```{r}
invisible(const_winner(2014))
```

This function creates and return a data.frame for the constructorStandings API for the years between 'from' and 'to'
```{r}
const_btw_years(2013,2015)
```

Gives the constructor with the most wins during a given period [from-to]
```{r}
invisible(const_winner_period(2010,2012))
```




